Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-21 paper.tex
Adds back some space, to shift Section 4 title
Add ACM bibstrip
Adds to-dos based on reviews

\toappear{}
\maketitle
%==================================================================================================
\begin{abstract}

@@

The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: It may itself
by played out, or it may be needed as part of the application's decoding chain.
For example, I frames provide utility both in being played out, and as
foundations for subsequent P and B frames. As a result, dependencies may take
higher priority than deadlines.
% : data may be sent even if it
% cannot be played out, if it is necessary for the decoding of other data.

@@

We note the importance of congestion control. %Clearly,
Historically real-time applications needed an isochronous channel,
and needed to avoid subjected to congestion control. This is impractical on the
Internet. Further, while some applications are non-adaptive or constant bitrate,
an increasing number are either or both of adaptive and variable bitrate. Users would be better served by
applications that to available bandwidth.

We note that a connection-oriented transport is a lesser, but useful,
requirement.
% for many real-time multimedia applications.
Indeed, flexibility to
change the destination within a call is beneficial for
applications that support mobile users, or for some forms of multiparty session.
However, to support NAT traversal and to help dynamically manage firewall
pinholes, it is often desirable for the transport to be connection oriented. We
believe these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service. Similarly, while not strictly
needed by the applications, it is beneficial if the transport provides a
keep-alive service to refresh NAT and firewall bindings if the application goes
silent.

@@

   \item Once the connection is established, the receiver
     indicates the its media play-out delay, in milliseconds, via
     the \texttt{set\_po\_delay()} call. This specifies the time that the
     application will buffer data, to compensate for network timing jitter,
     before it is rendered to the user. The play-out delay is fed back to
     the sender host, for use as part of the media deadline estimation.

@@

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
%\todo{expand, and discuss how this evolution has occurred to date}
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency. It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.

@@

@@

In order to maintain compatibility with middleboxes, offering partial
reliability requires using \emph{inconsistent retransmissions}. This means
that the mapping between message data and TCP sequence numbers is no longer
static: a given TCP sequence number may be relate to different messages at
different times. Therefore, an application-level sequence number is
required to allow messages to be uniquely identified.

@@

%==================================================================================================
\section{Realising Transport Services}
\label{sec:realising}

@@

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. Any message fragments are buffered,
alongside their TCP sequence number, awaiting the arrival of the remainder
of the message. Once the message has been reassembled, it is decoded, and
delivered to the application.

% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}

@@

QUIC \cite{draft-tsvwg-quic-protocol-02} demonstrates that similar services
can be provided by a new protocol running over UDP, while \cite{RFC6773} and
\cite{draft-ietf-rtcweb-data-channel-13} demonstrate that existing protocols,
DCCP and SCTP, can also be effectively tunnelled over UDP. Fallback to TCP
is discussed in this paper, and on our previous work \cite{mcquistin2016hollywood}.

>>>>

\CopyrightYear{2016} 
\setcopyright{acmlicensed}
\conferenceinfo{ANRW '16,}{July 16 2016, Berlin, Germany}
\isbn{978-1-4503-4443-2/16/07}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2959424.2959443}

\maketitle
%==================================================================================================
\begin{abstract}

@@

The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
For example, I frames provide utility both in being played out, and as
foundations for subsequent P and B frames. As a result, dependencies may take
higher priority than deadlines.
\todo{Review A: Some video-specific jargon (I, P, B frames) could be
expanded/explained.}
% : data may be sent even if it
% cannot be played out, if it is necessary for the decoding of other data.

@@

We note the importance of congestion control. %Clearly,
Historically real-time applications needed an isochronous channel,
and needed to avoid subjected to congestion control. This is impractical on the
Internet. Further, while some applications are non-adaptive or constant bitrate,
an increasing number are either or both of adaptive and variable bitrate.
Users would be better served by applications that adapt to available bandwidth.

We note that a connection-oriented transport is a lesser, but useful,
requirement.
% for many real-time multimedia applications.
Indeed, flexibility to
change the destination within a call is beneficial for
applications that support mobile users, or for some forms of multiparty session.
However, to support NAT traversal and to help dynamically manage firewall
pinholes, it is often desirable for the transport to be connection oriented. We
believe these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service. Similarly, while not strictly
needed by the applications, it is beneficial if the transport provides a
keep-alive service to refresh NAT and firewall bindings if the application goes
silent.
\todo{Review A: Indicate that connectionless protocols can create in-network
state.}

@@

   \item Once the connection is established, the receiver
     then indicates its media play-out delay, in milliseconds, via
     the \texttt{set\_po\_delay()} call. This specifies the time that the
     application will buffer data, to compensate for network timing jitter,
     before it is rendered to the user. The play-out delay is fed back to
     the sender host, for use as part of the media deadline estimation.

@@

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
%\todo{expand, and discuss how this evolution has occurred to date}
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency. It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.
\todo{Review A: Show how the API supports alternative congestion control
algorithms.}
\todo{Review B: Alternatives might have deployment challenges (e.g.,
fairness between delay and loss based algorithms).}

@@

\todo{Review A: Section 3 should also note that connectionless send and
receive already work on connection-oriented sockets}

@@

In order to maintain compatibility with middleboxes, offering partial
reliability requires using \emph{inconsistent retransmissions}. This means
that the mapping between message data and TCP sequence numbers is no longer
static: a given TCP sequence number may be relate to different messages at
different times. Therefore, an application-level sequence number is
required to allow messages to be uniquely identified.
\todo{Review B: Inconsistent retransmissions are not well introduced. Should
be more explicit, and earlier.}

@@

\todo{Review A: Section 4 should have a forward reference to section 5}
%==================================================================================================
\section{Realising Transport Services}
\label{sec:realising}

@@

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. Any message fragments are buffered,
alongside their TCP sequence number, awaiting the arrival of the remainder
of the message. Once the message has been reassembled, it is decoded, and
delivered to the application.
\todo{Review B: Head-of-line blocking problem not introduced, so not clear
why this mechanism is needed.}
% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}

@@

QUIC \cite{draft-tsvwg-quic-protocol-02} demonstrates that similar services
can be provided by a new protocol running over UDP, while \cite{RFC6773} and
\cite{draft-ietf-rtcweb-data-channel-13} demonstrate that existing protocols,
DCCP and SCTP, can also be effectively tunnelled over UDP. Fallback to TCP
is discussed in this paper, and on our previous work \cite{mcquistin2016tcp}.
